---
title: "Property prices in Venice, Florida"
author: "YOUR NAME (UUN: S0000000, GitHub: USERNAME)"
date: "`r paste0('Last Compiled: ',format(Sys.time(), '%d %B, %Y'))`"
output: html_document
---

```{r load-packages, message=FALSE, warning=FALSE}
library(tidyverse)
library(tidymodels)
```

## Exercise 1

```{r load-data, eval=FALSE}
# change eval=FALSE to eval=TRUE


# Add your code to load the data here

RealEstate <- ___

```


## Exercise 2 and 3

```{r add-variable , eval=FALSE}
# change eval=FALSE to eval=TRUE

RealEstate <- RealEstate %>%
  ___(Less_than_300k = case_when(
    ___,
    ___
    ),
    Less_than_300k = fct_relevel(Less_than_300k, ___, ___)
    )
  
RealEstate%>%
  ___(___) %>%
  ___(
    ___,
  )
``` 


---

## Exercise 4

```{r dataviz, eval=FALSE}
# change eval=FALSE to eval=TRUE
ggplot(____) +
  ____(____)

```

## Exercise 5

*Add your narrative here.*

---

## Exercise 6

```{r bootstrap, eval=FALSE}
# change eval=FALSE to eval=TRUE

boot_df <- RealEstate %>%
  # specify the variable of interest
  ___(___) %>% 
  # generate 10000 bootstrap samples
  ___(___) %>% 
  # calculate the mean of each bootstrap sample
  calculate(stat = ___) %>%
  # calculate 90% confidence interval
    summarize(lower = ___,
            upper = ___)

boot_df

```

---

## Exercise 7

#### Code

```{r linear-reg, eval=FALSE}
# change eval=FALSE to eval=TRUE

real_est_fit <- ___

tidy(log_real_est_fit)

```

#### Narrative

*Add your narrative here.*


## Exercise 8

#### Code

```{r linear-reg_simple, eval=FALSE}
# change eval=FALSE to eval=TRUE

# New model fit


```


```{r}
# Calculation of performance metrics

```

```{r}
# Plot the residual vs fitted values

```

#### Narrative

*Add your narrative here.*

## Exercise 9

#### Code

```{r log-reg, eval=FALSE}
# change eval=FALSE to eval=TRUE


log_real_est_fit <- ___


tidy(log_real_est_fit)

```


#### Narrative

*Add your narrative here.*

---

## Exercise 10

(a) Ethical issues with how the data was obtained/processed:

*Add your narrative here.*

(b) Ethical issues with how the data visualisation has been presented:

*Add your narrative here.*

